Bird beak's elaboration and innovation

### 2023-04-19 Analysis/04-Figure_with_ellipse__alternative.Rmd
Create 04-Figure_with_ellipse__alternative.Rmd

TODO:
 - [ ] split in two figures
 - [ ] make E/I boxes larger
 - [ ] make E/I colours always orange/blue

@@

>>>>

@@

```{r}
pdf(file = "test.pdf", height = 11.693, width = 8.268)
## Plot splitting
x <- 82
super_orders <- rbind(
      #"Paleognathae" = "Tinamiformes",  
      matrix(c(rep(1+x,  1), rep(2+x,  1), rep(3+x,  1)), 1, 3),
      #"Galloanserae" = c("Galliformes", "Anseriformes"),
      matrix(c(rep(4+x,  2), rep(5+x,  2), rep(6+x,  2)), 2, 3),
      #"Mirandornithes" = c("Podicipediformes"),
      matrix(c(rep(7+x,  1), rep(8+x,  1), rep(9+x,  1)), 1, 3),
      #"Columbimorphae" = c("Columbiformes", "Pterocliformes"),
      matrix(c(rep(10+x, 2), rep(11+x, 2), rep(12+x, 2)), 2, 3),
      #"Otidimorphae" = c("Otidiformes", "Cuculiformes", "Musophagiformes"),
      matrix(c(rep(13+x, 3), rep(14+x, 3), rep(15+x, 3)), 3, 3),
      #"Gruiformes" (NOT A SUPER ORDER)
      matrix(0, 1, 3),
      #"Aequornithes" = c("Procellariiformes", "Sphenisciformes", "Ciconiiformes", "Pelecaniformes", "Suliformes"),
      matrix(c(rep(16+x, 5), rep(17+x, 5), rep(18+x, 5)), 5, 3),
      #"Strisores" = c("Caprimulgiformes", "Apodiformes"),
      matrix(c(rep(19+x, 2), rep(20+x, 2), rep(21+x, 2)), 2, 3),
      #"Charadriiformes" (NOT A SUPER ORDER)
      matrix(0, 1, 3),
      #"Telluraves" = c("Trogoniformes", "Bucerotiformes", "Coraciiformes", "Piciformes", "Strigiformes", "Accipitriformes", "Falconiformes", "Psittaciformes", "Passeriformes")
      matrix(c(rep(22+x, 9), rep(23+x, 9), rep(24+x, 9)), 9, 3))

layout_matrix <- cbind( 
                matrix(1, 27, 1), # first column
                matrix(seq(1:(27*3))+1, 27, 3, byrow = TRUE), # second/third column
                super_orders)

widths_vals <- c(5, 1, 1, 1, 1, 1, 1)
height_vals <- rep(1, 27)
layout_spiro <- layout(layout_matrix, widths = widths_vals, heights = height_vals, respect = TRUE)
# layout.show(layout_spiro)

## Plotting the tree
tip_order <- c(
    "Tinamiformes"= 1,
    "Galliformes"= 3,
    "Anseriformes"= 2,
    "Otidiformes"= 7,
    "Cuculiformes" = 8,
    "Gruiformes" = 9, 
    "Musophagiformes" = 10,
    "Procellariiformes" = 12,
    "Sphenisciformes" = 11,
    "Ciconiiformes" = 13,
    "Pelecaniformes"= 15,
    "Suliformes" = 14,
    "Podicipediformes" = 4,
    "Columbiformes" = 6,
    "Pterocliformes" = 5,
    "Charadriiformes" = 18,
    "Trogoniformes" = 21,
    "Bucerotiformes" = 22,
    "Coraciiformes" = 23,
    "Piciformes" = 24,
    "Strigiformes" = 20,
    "Accipitriformes" = 19, 
    "Falconiformes" = 25,
    "Psittaciformes" = 26,
    "Passeriformes" = 27,
    "Caprimulgiformes" = 16, 
    "Apodiformes" = 17)

## Plotting each ellipse
for(i in 1:27) {
    wrap.plot.ellipses(i, tip_colours_orders, order_shapespace, results$order_results_between, ei.col = c("orange", "blue"), phylo.plot = TRUE)
}
load(file = "../Data/Processed/tip_colours_super_orders.rda")
for(i in 1:8) {
    ## Plot each pannel
    wrap.plot.ellipses(i, tip_colours_super_orders, superorder_shapespace, results$super_results_between, ei.col = c("orange", "blue"), phylo.plot = TRUE)
}
dev.off()

# ## Plotting the ellipses for each order
# for(i in 1:length(tip_order)) {
#     ## Plot each pannel
#     wrap.plot.ellipses(i, tip_colours_super_orders, superorder_shapespace, results$super_results_between, ei.col = c("orange", "blue"))
# }
